Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
fixed

We will first describe the flow a typical user would take when using this application. The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}

@@

[Therapist Portal Implementation Details Here]

>>>>

We will first describe the flow a typical user would take when using this application. The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}

@@

\subsubsection{Component 1}

\subsubsection{Component 2}

\subsubsection{Component 3}
